### 2016-03-21 docs/ms_communitySynchrony.Rmd
adds number of refs to title page
adds color formatting for coauthor review of sections

\textit{Keywords}: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability

@@

\textbf{Number of References}:

@@

#### Simulation experiments
We performed removal simulation experiments where drivers (environmental stochasticity, demographic stochasticity, or interspecific competition) were removed one-by-one and in combination.
To remove interspecific interactions, we set the off-diagonals of the interaction matrix for each vital rate regression to zero.
This retains intraspecific interactions, and thus density-dependence, and results in simulations where species are effectively growing in monoculture.
To remove the effect of a fluctuating environment, we removed the temporal (interannual) random effects from the regression equations.
To remove the effect of demographic stochasticity, we use the IPM rather than the IBM because the IPM does not include demographic stochasticity (demographic stochasticity cannot be removed from the IBM).
Since the effect of demographic stochasticity on population dynamics depends on population size [@Lande2003], we can control the strength of demographic stochasticity by simulating the IBM on areas (e.g. plots) of different size.
Indeed, results from an IBM with infinite population size would equal results from the IPM.
Given computational constraints, the largest landscape we simulate is a 5 square meter plot.

@@

RESULTS
-------
Synchrony of species' per capita growth rates at our study sites ranged from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to 0.92 (Table 2).
Synchrony tended to be higher in communities with few species (Arizona and New Mexico) and/or with relatively high temporal variability in percent cover (e.g., Montana).
Synchrony was lowest in Idaho, the only data set that includes two life forms: a shrub and three perennial grasses (Table 1).
For all five communities, species synchrony from IPM and IBM simulations closely approximated observed synchrony (Fig. S1).
IBM-simulated synchrony is consistently, but only slightly, lower than IPM-simulated synchrony (Fig. S1), likely due to the desynchronizing effect of demographic stochasticity.

@@

Simulation experiments revealed that removing environmental fluctuations has the largest impact on synchrony, leading to a reduction in synchrony of species growth rates in four out of five communities (Fig. 1).
Removing environmental fluctuations ("No E.S" simulations) decreased synchrony by 33% in Arizona, 48% in Kansas, 39% in Montana, and 40% in New Mexico.
Only in Idaho did removing environmental fluctuations cause an increase in synchrony (Fig. 1), but the effect was small (9% increase; Table S1).
Overall, species' temporal random effects in the statistical vital rate models are positively correlated (Table S2).
Species interactions are weak in these communities [Table S3 and @Chu2015], and removing interspecific competition had little effect on synchrony (Fig. 1; "No Comp." simulations).
Removing competition caused, at most, a 5% change in synchrony (Fig. 1).
Removing demographic stochasticity ("No D.S." simulations) caused synchrony to increase slightly in all communities (Fig. 1), with an average 6% increase over synchrony from IBM simulations on a five meter area.
The desynchronizing effect of demographic stochasticity modestly counteracted the synchronizing force of the environment, but not enough to lower synchrony to the level observed when only demographic stochasticity is operating (Fig. 2).
For all five communities, the synchrony of species' growth rates in monoculture almost perfectly matched species synchrony in polyculture (Fig. 3).
Results for synchrony of percent cover are qualitatively similar (Figs. S2-S3) but more variable, as expected by theory [@Loreau2008a].

@@

Our analysis of how demographic stochasticity affects synchrony across population sizes also demonstrates that synchrony depends on the observation area.
As the observation area increases, population size increases and the desynchronizing effect of demographic stochasticity lessens (Fig. 2).
Thus, our results suggest that community-wide species synchrony will increase as the observation area increases, rising from $\mathcal{M}_D$ to $\mathcal{M}_E$.
Such a conclusion assumes, however, that species richness remains constant as observation area increases, which is unlikely [@Taylor1961].
Recent theoretical work has begun to explore the linkage between ecosystem stability and spatial scale [@Wang2014; @Wang2016], and our results suggest that including demographic stochasticity in theoretical models of metacommunity dynamics may be important for understanding the role of species synchrony in determining ecosystem stability across spatial scales.

@@

### Interspecific interactions had little impact on community synchrony
We expected community synchrony of per capita growth rates to decrease when we removed interspecific interactions [@Loreau2008a and Supplementary Information].
We found that community synchrony was virtually indistinguishable between simulations with and without interspecific interactions (Fig. 2).
The lack of an effect of interspecific competition on synchrony is in contrast to a large body of theoretical work that predicts a strong role for competition in creating compensatory dynamics [@Tilman1988] and a recent empirical analysis [@Gross2014].

@@

CONCLUSIONS
-----------
Species-specific responses to temporally fluctuating environmental conditions is an important mechanism underlying asynchronous population dynamics and, in turn, ecosystem stability [@Loreau2013].
When we removed environmental variation, we found that synchrony decreased in four out of the five grassland communities we studied (Fig. 2).
A tempting conclusion is that our study confirms that compensatory dynamics are rare in natural communities, and that ecologically-similar species will exhibit synchronous dynamics [e.g., @Houlahan2007].
Such a conclusion is only half correct.
The perennial grasses we studied do have similar responses to the environment (Table S2), which will tend to synchronize dynamics.
However, if community-wide species synchrony is less than 1, as it is in all our focal communities, some degree of compensatory dynamics must be present [@Loreau2008a].
In agreement with other studies [@Rocha2011; @Vasseur2014], we find that environmental responses are primarily responsible for the degree of synchrony among ecologically-similar species.
Such a conclusion is in contrast to a recent analysis of several biodiversity-ecosystem functioning experiments showing that competition drives community synchrony [@Gross2014].
Recently assembled communities, such as experimental plots, may exhibit strong species interactions that will weaken over time [@Kokkoris1999].
Future research on the influence of community assembly on synchrony could reconcile inconsistent observations on the biotic and abiotic forces that jointly drive community dynamics.

>>>>

\textbf{Keywords}: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability

@@

\textbf{Number of References}: 46

@@

#### Simulation experiments
We performed removal simulation experiments where drivers (environmental stochasticity, demographic stochasticity, or interspecific competition) were removed one-by-one and in combination.
To remove interspecific interactions, we set the off-diagonals of the interaction matrix for each vital rate regression to zero.
This retains intraspecific interactions, and thus density-dependence, and results in simulations where species are effectively growing in monoculture.
To remove the effect of a fluctuating environment, we removed the temporal (interannual) random effects from the regression equations.
To remove the effect of demographic stochasticity, we use the IPM rather than the IBM because the IPM does not include demographic stochasticity (demographic stochasticity cannot be removed from the IBM).
Since the effect of demographic stochasticity on population dynamics depends on population size [@Lande2003], we can control the strength of demographic stochasticity by simulating the IBM on areas (e.g. plots) of different size.
\textcolor{red}{Indeed, results from an IBM with infinite population size would equal results from the IPM.
Given computational constraints, the largest landscape we simulate is a 5 square meter plot.}

@@

### Results
Synchrony of species' per capita growth rates at our study sites ranged from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to 0.92 (Table 2).
Synchrony tended to be higher in communities with few species (Arizona and New Mexico) and/or with relatively high temporal variability in percent cover (e.g., Montana).
Synchrony was lowest in Idaho, the only data set that includes two life forms: a shrub and three perennial grasses (Table 1).
For all five communities, species synchrony from IPM and IBM simulations closely approximated observed synchrony (Fig. S1).
IBM-simulated synchrony is consistently, but only slightly, lower than IPM-simulated synchrony (Fig. S1), likely due to the desynchronizing effect of demographic stochasticity.

@@

Simulation experiments revealed that removing environmental fluctuations has the largest impact on synchrony, leading to a reduction in synchrony of species growth rates in four out of five communities (Fig. 1).
Removing environmental fluctuations ("No E.S" simulations) decreased synchrony by 33% in Arizona, 48% in Kansas, 39% in Montana, and 40% in New Mexico.
Only in Idaho did removing environmental fluctuations cause an increase in synchrony (Fig. 1), but the effect was small (9% increase; Table S1).
Overall, species' temporal random effects in the statistical vital rate models are positively correlated (Table S2).
Species interactions are weak in these communities [Table S3 and @Chu2015], and removing interspecific competition had little effect on synchrony (Fig. 1; "No Comp." simulations).
Removing competition caused, at most, a 5% change in synchrony (Fig. 1).
Removing demographic stochasticity ("No D.S." simulations) caused synchrony to increase slightly in all communities (Fig. 1), with an average 6% increase over synchrony from IBM simulations on a five meter area.
\textcolor{red}{The desynchronizing effect of demographic stochasticity, which increases as population size decreases, modestly counteracted the synchronizing force of the environment, but not enough to lower synchrony to the level observed when only demographic stochasticity is operating (Fig. 2).
Synchrony from simulations with demographic and environmental stochasticity decreased as the simulated area decreased, representing a shift from synchrony being driven by environmental responses (e.g., $\mathcal{M}_E$) to being driven by a combination of demographic and environmental stochasticity (e.g., between $\mathcal{M}_E$ and $\mathcal{M}_D$).}
For all five communities, the synchrony of species' growth rates in monoculture almost perfectly matched species synchrony in polyculture (Fig. 3).
Results for synchrony of percent cover are qualitatively similar (Figs. S2-S3) but more variable, as expected by theory [@Loreau2008a].

@@

\textcolor{red}{Our analysis of how demographic stochasticity affects synchrony across population sizes also demonstrates that synchrony depends on the observation area.
As the observation area increases, population size increases and the desynchronizing effect of demographic stochasticity lessens (Fig. 2).
Thus, our results suggest that community-wide species synchrony will increase as the observation area increases, rising from $\mathcal{M}_D$ to $\mathcal{M}_E$.
Such a conclusion assumes, however, that species richness remains constant as observation area increases, which is unlikely [@Taylor1961].
Recent theoretical work has begun to explore the linkage between ecosystem stability and spatial scale [@Wang2014; @Wang2016], and our results suggest that including demographic stochasticity in theoretical models of metacommunity dynamics may be important for understanding the role of species synchrony in determining ecosystem stability across spatial scales.}

@@

### Interspecific interactions had little impact on community synchrony
We expected community synchrony of per capita growth rates to decrease when we removed interspecific interactions [@Loreau2008a].
We found that community synchrony was virtually indistinguishable between simulations with and without interspecific interactions (Fig. 2).
The lack of an effect of interspecific competition on synchrony is in contrast to a large body of theoretical work that predicts a strong role for competition in creating compensatory dynamics [@Tilman1988] and a recent empirical analysis [@Gross2014].

@@

CONCLUSIONS
-----------
Species-specific responses to temporally fluctuating environmental conditions is an important mechanism underlying asynchronous population dynamics and, in turn, ecosystem stability [@Loreau2013].
When we removed environmental variation, we found that synchrony decreased in four out of the five grassland communities we studied (Fig. 2).
\textcolor{blue}{A tempting conclusion is that our study confirms that compensatory dynamics are rare in natural communities, and that ecologically-similar species will exhibit synchronous dynamics [e.g., @Houlahan2007].
Such a conclusion is only half correct.
The perennial grasses we studied do have similar responses to the environment (Table S2), which will tend to synchronize dynamics.
However, if community-wide species synchrony is less than 1, as it is in all our focal communities, some degree of compensatory dynamics must be present [@Loreau2008a].}
In agreement with other studies [@Rocha2011; @Vasseur2014], we find that environmental responses are primarily responsible for the degree of synchrony among ecologically-similar species.
Such a conclusion is in contrast to a recent analysis of several biodiversity-ecosystem functioning experiments showing that competition drives community synchrony [@Gross2014].
Recently assembled communities, such as experimental plots, may exhibit strong species interactions that will weaken over time [@Kokkoris1999].
Future research on the influence of community assembly on synchrony could reconcile inconsistent observations on the biotic and abiotic forces that jointly drive community dynamics.
